---
title: "Fish Selectivity"
author: "Meghan Duffy"
date: "2/28/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plot of data collected in 2002-2003 on selectivity of fish predation on infected Daphnia
Raw data are available in photocopies of lab notebooks.
Data used in this file are taken from a Systat file that was originally created back when first analyzed data (e.g., for Duffy et al. 2005 L&O and for Duffy & Hall 2008 AmNat)

```{r,load libraries,message=FALSE,echo=FALSE}
library(ggplot2)
library(dplyr)
library(cowplot)
library(stringr)
```

```{r, import data}
fish <- read.csv("FishSummary20022003_forR.csv", na.strings = "?")
head(fish)
colnames(fish)
str(fish)
```

```{r, make plot for metsch}
metschplot <- fish %>%
  filter(Comparison ==c("Metsch")) %>%
  ggplot(aes(x=Infected,y=Alpha,fill=Host,shape=Lake)) +
  geom_point() +
  ylab("Chesson's alpha") +
  theme_bw()

metschplot
```

```{r, make plot for all parasites leaving off uninfected data}
fullplot <- fish %>%
  filter(Infected ==c("Infected")) %>%
  ggplot(aes(x=Parasite,y=Alpha,colour=Host,shape=Lake)) +
  scale_colour_manual(values=c("black","gray")) +
  geom_point(size=4) +
  ylab("Chesson's alpha") +
  scale_y_continuous(limits=c(0.5,1.0)) +
  geom_hline(yintercept = 0.5, linetype="dotted") 

fullplot

save_plot("fullplot.jpg", fullplot, base_height=4, base_width = 6)
```

## Now looking at data on spore retrieval after fish gut passage

```{r, import spore data}
spore <- read.csv("FishGutPassageSummary20042012.csv", na.strings = "?")
head(spore)
colnames(spore)
str(spore)
```
```{r, make plot for all spore recovery data}
metschsporeplot <- spore %>%
  filter(Parasite==c("Metsch")) %>%
  ggplot(aes(x=Source,y=sporesperdaphnia)) +
  geom_point(size=4,position=position_jitter(w=0.3, h = 0.0)) +
  ylab("Spores per Daphnia") +
  ggtitle("Metschnikowia")

pastsporeplot <- spore %>%
  filter(Parasite==c("Pasteuria")) %>%
  ggplot(aes(x=Source,y=sporesperdaphnia)) +
  geom_point(size=4) +
  ylab("Spores per Daphnia") +
  ggtitle("Pasteuria")

combinedplot <- ggdraw() +
  draw_plot(metschsporeplot,0,0,0.6,1.0) +
  draw_plot(pastsporeplot,0.6,0,0.4,1.0) 

combinedplot

save_plot("combinedplot.jpg", combinedplot)
```

```{r, make boxplots for all spore recovery data}
metschsporeboxplot <- spore %>%
  filter(Parasite==c("Metsch")) %>%
  ggplot(aes(x=Source,y=sporesperdaphnia)) +
  geom_boxplot() +
  ylab("Spores per Daphnia") +
  ggtitle("Metschnikowia")

pastsporeboxplot <- spore %>%
  filter(Parasite==c("Pasteuria")) %>%
  ggplot(aes(x=Source,y=sporesperdaphnia)) +
  geom_boxplot() +
  ylab("Spores per Daphnia") +
  ggtitle("Pasteuria")

combinedboxplot <- ggdraw() +
  draw_plot(metschsporeboxplot,0,0,0.6,1.0) +
  draw_plot(pastsporeboxplot,0.6,0,0.4,1.0) 

combinedboxplot

save_plot("combinedboxplot.jpg", combinedboxplot, base_height=4, base_width = 8)
```
## Finally, make a plot showing the infectivity of the spores retrieved from fish fecal pellets

```{r, import data on infectivity after gut passage}
inf <- read.csv("FishGutPassageInfectivitySummary20042012.csv", na.strings = "?")
head(inf)
colnames(inf)
str(inf)
```
```{r, stats on spore yield after fish gut passage}
spore %>%
  filter(Parasite==c("Metsch")) %>%
  group_by(Source) %>%
  summarise(mean=mean(sporesperdaphnia),median=median(sporesperdaphnia))

spore %>%
  filter(Parasite==c("Pasteuria")) %>%
  group_by(Source) %>%
  summarise(mean=mean(sporesperdaphnia),median=median(sporesperdaphnia))

pastspores <- subset(spore,Parasite==c("Pasteuria"))
t.test(pastspores$sporesperdaphnia ~ pastspores$Treatment)
```
  
```{r, make plot for all spore infectivity data}
infplot <- inf %>%
  ggplot(aes(x=Parasite,y=AvgPropInf,color=Treatment)) +
  scale_colour_manual(values=c("#000000","#999999")) +
  geom_boxplot() +
  ylab("Proportion infected") 

infplot

save_plot("infplot.jpg", infplot, base_height=4, base_width = 6)
```

